---
title: "Benchmark of all integration tools with noise for the supervised integration"
author: "Leonard Herault"
date: '2022-12-09'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## libraries

```{r cars}
library(ggplot2)
library(Seurat)
library(ggrepel)
```

```{bash}
#cp visualization/scIB_knit_table.R ../scib-pipeline/reports/
#mv scIB_knit_table.R knit_table.R
```

```{r}
# install.packages('dynutils')
# install.packages('magick')
# install.packages('cowplot')
# install.packages("ggforce")
# install.packages('ggimage')
# install.packages('Hmisc')
# install.packages("plyr")
#source('../../scib-reproducibility/visualization/plotSingleTaskRNA.R')


library(tibble)
library(RColorBrewer)
library(dynutils)
library(stringr)
library(Hmisc)
library(plyr)


source("knit_table.R") # Please put knit_table.R in your working dir

source("R_fun_report.R")

tasks <- c("human_pancreas", "lung_atlas", "immune_cell_hum","tcells_atlas")
labels = c("Pancreas", "Lung", "Immune (hum)",'T cells')

#labels_RNA = c("Pancreas", "Lung", "Immune (hum)",'Immune (hum, mou)', 'T cells')
```

```{r}
library(STACAS)
library(Seurat)
library(scIntegrationMetrics)
library(anndata)
```

This report required the files :
- `../data/metrics_R.csv`
- `../data/metrics.csv`
generated with the snakemake pipeline that are available in the `results` folder of the repository (you can simply copy paste them in a folder data at the root of the repository).

It also required the files (already available here in the repository) :
- `./scalability_score_memory_revision.csv`
- `./scalability_score_memory_revision.csv`
generated by the jupyter notebook `scalability_assessment.ipynb` from the file `../data/benchmarks.csv` (we also provide it in the results folder of this repository) 


```{r}
misRateTable <- data.frame()
celltypeLabel = c("celltype","celltype","final_annotation","final_annotation","cell_type")
names(celltypeLabel) <- c('tcells_atlas','human_pancreas','immune_cell_hum','immune_cell_hum_mou',"lung_atlas")

atlases <- c('tcells_atlas','human_pancreas','immune_cell_hum',"lung_atlas")

for (task in atlases) {
  adata <- read_h5ad(paste0("../data/",task,"/prepare/unscaled/hvg/adata_pre.h5ad"))
  
  misRate <- table(adata$obs[,paste0('unknown_15_shuffling_20_',celltypeLabel[task])] != as.vector(adata$obs[,celltypeLabel[task]]))["TRUE"]/length(adata$obs[,celltypeLabel[task]])
  unknownRate <- table(adata$obs[,paste0('unknown_15_shuffling_20_',celltypeLabel[task])] == "unknown")["TRUE"]/length(adata$obs[,celltypeLabel[task]])
  misRateTable <- rbind(misRateTable,c(task, 'unknown_15_shuffling_20', misRate,unknownRate))
  
}
colnames(misRateTable) <- c("task","'alteration'","percentMislabelling","percentUnknown")
misRateTable$percentMislabelling <- as.numeric(misRateTable$percentMislabelling)
misRateTable$percentUnknown <- as.numeric(misRateTable$percentUnknown)

ggplot(misRateTable, aes(x = task , y = percentMislabelling, fill = task)) + geom_bar(stat="identity", color="black", position=position_dodge())

ggplot(misRateTable, aes(x = task , y = percentUnknown, fill = task)) + geom_bar(stat="identity", color="black", position=position_dodge())
```

```{r}
metricsR <- read.csv("../data/metrics_R.csv",row.names = 1)

scenarios <- str_split_fixed(rownames(metricsR),pattern = "/",n=7)
head(scenarios)

scenarios <- scenarios[,-1]
colnames(scenarios) <- c("task","noise","folder","scaling","features","method")
metricsR <- cbind(scenarios,metricsR)

metricsR$method <- str_split_fixed(metricsR$method,pattern = "/",n=2)[,2]
metricsR$output <- str_split_fixed(metricsR$method,pattern = "_",n=2)[,2]
metricsR$tool <- str_split_fixed(metricsR$method,pattern = "_",n=2)[,1]

head(metricsR)
```

```{r}
metrics <- read.csv("../data/metrics.csv",row.names = 1)


scenarios <- str_split_fixed(rownames(metrics),pattern = "/",n=7)
head(scenarios)

scenarios <- scenarios[,-1]
colnames(scenarios) <- c("task","noise","folder","scaling","features","method")
metrics <- cbind(scenarios,metrics)

metrics$output <- str_split_fixed(metrics$method,pattern = "_",n=2)[,2]
metrics$tool <- str_split_fixed(metrics$method,pattern = "_",n=2)[,1]

head(metrics)

```

```{r}
rownames(metricsR) <- gsub(rownames(metricsR),pattern = "/R/",replacement = "/")
metrics <- cbind(metrics, metricsR[rownames(metrics),c("CiLISI","CiLISI_means")])
metrics$ASW_label_raw <- 2*metrics$ASW_label - 1

metrics$methodLong <- paste(metrics$method,metrics$scaling,sep = "_")

```

```{r fig.width=3.5,fig.width=3.5}
methodToCompare <- c("STACAS_embed_unscaled","STACAS_embed_scaled",
                     "semiSupSTACAS_embed_unscaled","semiSupSTACAS_embed_scaled",
                     "seuratrpca_embed_unscaled","seuratrpca_embed_scaled",
                     "seurat_embed_unscaled","seurat_embed_scaled",
                     "fastmnn_embed_scaled","fastmnn_embed_unscaled",
                     "harmony_embed_unscaled","harmony_embed_scaled",
                     "scvi_embed_unscaled",
                     "scanorama_embed_scaled","scanorama_embed_unscaled",
                     "scanvi_embed_unscaled",
                     "combat_full_scaled","combat_full_unscaled",
                     "scgen_full_unscaled","unintegrated_full_unscaled"
)
for (t in unique(metrics$task)) {
  for (n in unique(metrics$noise)) {
    metricsSub <- metrics[metrics$noise == n & metrics$task == t,]
  plot(ggplot(metricsSub[metricsSub$methodLong %in% methodToCompare,],
              aes(x = CiLISI,color=tool,y=ASW_label_raw,shape= scaling)) +geom_point() + facet_wrap(c("task","noise"),scales = "free",ncol = 2) +
         geom_label_repel(aes(label = paste0(tool,"_",scaling)),
                          box.padding   = 0.35, 
                          point.padding = 0.5,
                          segment.color = 'grey50') + NoLegend())
  }
}
```

## Saving PDF

```{r}
dir.create("pdf/CiLISI_vs_ASW_label",recursive = T)
for (t in unique(metrics$task)) {
  pdf(file = paste0("pdf/CiLISI_vs_ASW_label/",t,"_CiLISI_vs_ASW_label.pdf"),width = 8, height = 8)
  for (n in unique(metrics$noise)) {
    metricsSub <- metrics[metrics$noise == n & metrics$task == t,]
  plot(ggplot(metricsSub[metricsSub$methodLong %in% methodToCompare,],
              aes(x = CiLISI,color=tool,y=ASW_label_raw,shape= scaling)) +geom_point() + facet_wrap(c("task","noise"),scales = "free",ncol = 2) +
         geom_label_repel(aes(label = paste0(tool,"_",scaling)),
                          box.padding   = 0.35, 
                          point.padding = 0.5,
                          segment.color = 'grey50') + NoLegend())
  }
}
```

```{r}
library(ggpubr)

ggplot(metrics[metrics$methodLong %in% methodToCompare,],aes(x=kBET,y=CiLISI)) + geom_point() + facet_wrap("~task") + stat_cor()

ggplot(metrics[metrics$methodLong %in% methodToCompare,],aes(x=iLISI,y=CiLISI)) + geom_point() + facet_wrap("~task") + stat_cor()

```

```{r}

ggplot(metrics[metrics$methodLong %in% methodToCompare,],aes(x=kBET,y=CiLISI)) + geom_point() + facet_wrap("~task") + stat_cor(method = "spearman")

ggplot(metrics[metrics$methodLong %in% methodToCompare,],aes(x=iLISI,y=CiLISI)) + geom_point() + facet_wrap("~task") + stat_cor(method = "spearman")
```


# Only CiLISI and ASW_label different normalisation, no gene matrix for seurat based methods,

## 15% Unknown 20% shuflled labels
```{r}
metricsCiLISIlabelASW <- metrics[!metrics$method %in% c("seuratrpca_full","semiSupSTACAS_full","STACAS_full","seurat_full","fastmnn_full")& metrics$noise == "unknown_15_shuffling_20",]
metricsCiLISIlabelASW <- metricsCiLISIlabelASW[,c("CiLISI","ASW_label")]

#metricsCiLISIlabelASW <- metricsCiLISIlabelASW[,c("CiLISI","ASW_label_raw")] 

#metricsCiLISIlabelASW$ASW_label_raw[metricsCiLISIlabelASW$ASW_label_raw < 0] <- 0

colnames(metricsCiLISIlabelASW) <- c("iLISI","ASW_label")
dir.create("CiLISIlabelASW/singleTask",recursive = T)
dir.create("CiLISIlabelASW/best")

# remove noise info in rowname to directly use luecken function

rownames(metricsCiLISIlabelASW) <- gsub(rownames(metricsCiLISIlabelASW), pattern = "/unknown_15_shuffling_20/", replacement = "/")

dir.create("unknown_15_shuffling_20/CiLISIlabelASW/singleTask",recursive = T)
dir.create("unknown_15_shuffling_20/CiLISIlabelASW/best")

write.csv(metricsCiLISIlabelASW,"unknown_15_shuffling_20/CiLISIlabelASW/metrics.csv",col.names = T)


plotBestMethodsRNA(
  csv_metrics_path = "unknown_15_shuffling_20/CiLISIlabelASW/metrics.csv",
  outdir = "unknown_15_shuffling_20/CiLISIlabelASW/",
  # csv_usability_path = "./data/usability4bestMethods.csv",
  #csv_scalability_time_path = "./scalability_score_time_revision.csv",
  #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
  ids_RNA = tasks,
  #ids_simulation = c("simulations_1_1", "simulations_2"),  
  labels_RNA = labels,
  #labels_simulation = c("Sim 1", "Sim 2"), 
  weight_batch = 0.4,
  keepBest = F, keepBestOutput = F
)


plotBestMethodsRNA(
  csv_metrics_path = "unknown_15_shuffling_20/CiLISIlabelASW/metrics.csv",
  outdir = "unknown_15_shuffling_20/CiLISIlabelASW/best",
  # csv_usability_path = "./data/usability4bestMethods.csv",
  #csv_scalability_time_path = "./scalability_score_time_revision.csv",
  #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
  ids_RNA = tasks,
  #ids_simulation = c("simulations_1_1", "simulations_2"),  
  labels_RNA = labels,
  #labels_simulation = c("Sim 1", "Sim 2"), 
  weight_batch = 0.4,
  keepBest = T, keepBestOutput = T
)



plotSingleTaskRNA("unknown_15_shuffling_20/CiLISIlabelASW/metrics.csv",outdir = "unknown_15_shuffling_20/CiLISIlabelASW/singleTask")

```

```{r}
# To show shrinkage of scaled score because of fastmnn full output

# metricsCiLISIlabelASW_all <- metrics[,c("CiLISI","ASW_label")]
# 
# #metricsCiLISIlabelASW <- metricsCiLISIlabelASW[,c("CiLISI","ASW_label_raw")] 
# 
# #metricsCiLISIlabelASW$ASW_label_raw[metricsCiLISIlabelASW$ASW_label_raw < 0] <- 0
# 
# colnames(metricsCiLISIlabelASW_all) <- c("iLISI","ASW_label")
# dir.create("CiLISIlabelASW_all/singleTask",recursive = T)
# dir.create("CiLISIlabelASW_all/best")
# 
# 
# rownames(metricsCiLISIlabelASW_all) <- gsub(rownames(metricsCiLISIlabelASW_all), pattern = "/unknown_15_shuffling_20/", replacement = "/")
# 
# 
# 
# write.csv(metricsCiLISIlabelASW_all,"CiLISIlabelASW_all/metrics.csv",col.names = T)
# 
# 
# plotBestMethodsRNA(
#   csv_metrics_path = "CiLISIlabelASW_all/metrics.csv",
#   outdir = "CiLISIlabelASW_all",
#   # csv_usability_path = "./data/usability4bestMethods.csv",
#   #csv_scalability_time_path = "./scalability_score_time_revision.csv",
#   #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
#   ids_RNA = c("human_pancreas", "lung_atlas", "immune_cell_hum","immune_cell_hum_mou","tcells_atlas"),
#   #ids_simulation = c("simulations_1_1", "simulations_2"),  
#   labels_RNA = c("Pancreas", "Lung", "Immune (hum)",'Immune (hum, mou)', 'T cells'),
#   #labels_simulation = c("Sim 1", "Sim 2"), 
#   weight_batch = 0.4,
#   keepBest = F, keepBestOutput = F
# )
# 
# 
# plotBestMethodsRNA(
#   csv_metrics_path = "CiLISIlabelASW_all/metrics.csv",
#   outdir = "CiLISIlabelASW_all/best",
#   # csv_usability_path = "./data/usability4bestMethods.csv",
#   #csv_scalability_time_path = "./scalability_score_time_revision.csv",
#   #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
#   ids_RNA = c("human_pancreas", "lung_atlas", "immune_cell_hum","immune_cell_hum_mou","tcells_atlas"),
#   #ids_simulation = c("simulations_1_1", "simulations_2"),  
#   labels_RNA = c("Pancreas", "Lung", "Immune (hum)",'Immune (hum, mou)', 'T cells'),
#   #labels_simulation = c("Sim 1", "Sim 2"), 
#   weight_batch = 0.4,
#   keepBest = T, keepBestOutput = T
# )
# 
# 
# 
# plotSingleTaskRNA("CiLISIlabelASW_all/metrics.csv",outdir = "CiLISIlabelASW_all/singleTask")

```

```{r}
oriMetrics <- colnames(read.csv("../data/metrics.csv",row.names = 1))
oriMetrics <- oriMetrics[oriMetrics != "hvg_overlap"]

metricsMethodOK <- metrics[!metrics$method %in% c("seuratrpca_full","semiSupSTACAS_full","STACAS_full","seurat_full","fastmnn_full")& metrics$noise == "unknown_15_shuffling_20",
                           oriMetrics]

#metricsCiLISIlabelASW <- metricsCiLISIlabelASW[,c("CiLISI","ASW_label_raw")] 

#metricsCiLISIlabelASW$ASW_label_raw[metricsCiLISIlabelASW$ASW_label_raw < 0] <- 0

rownames(metricsMethodOK) <- gsub(rownames(metricsMethodOK), pattern = "/unknown_15_shuffling_20/", replacement = "/")



dir.create("unknown_15_shuffling_20/oriMetrics/singleTask",recursive = T)
dir.create("unknown_15_shuffling_20/oriMetrics/best")

write.csv(metricsMethodOK,"unknown_15_shuffling_20/oriMetrics/metrics.csv",col.names = T)


plotBestMethodsRNA(
  csv_metrics_path = "unknown_15_shuffling_20/oriMetrics/metrics.csv",
  outdir = "unknown_15_shuffling_20/oriMetrics",
  # csv_usability_path = "./data/usability4bestMethods.csv",
  #csv_scalability_time_path = "./scalability_score_time_revision.csv",
  #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
  ids_RNA = tasks,
  #ids_simulation = c("simulations_1_1", "simulations_2"),  
  labels_RNA = labels,
  #labels_simulation = c("Sim 1", "Sim 2"), 
  weight_batch = 0.4,
  keepBest = F, keepBestOutput = F
)


plotBestMethodsRNA(
  csv_metrics_path = "unknown_15_shuffling_20/oriMetrics/metrics.csv",
  outdir = "unknown_15_shuffling_20/oriMetrics/best",
  # csv_usability_path = "./data/usability4bestMethods.csv",
  #csv_scalability_time_path = "./scalability_score_time_revision.csv",
  #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
  ids_RNA = tasks,
  #ids_simulation = c("simulations_1_1", "simulations_2"),  
  labels_RNA = labels,
  #labels_simulation = c("Sim 1", "Sim 2"), 
  weight_batch = 0.4,
  keepBest = T, keepBestOutput = T
)



plotSingleTaskRNA("unknown_15_shuffling_20/oriMetrics/metrics.csv",outdir = "unknown_15_shuffling_20/oriMetrics/singleTask")

```

## broad annotations
```{r}
metricsCiLISIlabelASW <- metrics[!metrics$method %in% c("seuratrpca_full","semiSupSTACAS_full","STACAS_full","seurat_full","fastmnn_full")& metrics$noise == "broad",]
metricsCiLISIlabelASW <- metricsCiLISIlabelASW[metricsCiLISIlabelASW$task %in% c("immune_cell_hum","tcells_atlas"),]
metricsCiLISIlabelASW <- metricsCiLISIlabelASW[,c("CiLISI","ASW_label")]

#metricsCiLISIlabelASW <- metricsCiLISIlabelASW[,c("CiLISI","ASW_label_raw")] 

#metricsCiLISIlabelASW$ASW_label_raw[metricsCiLISIlabelASW$ASW_label_raw < 0] <- 0

# remove noise info in rowname to directly use luecken function

rownames(metricsCiLISIlabelASW) <- gsub(rownames(metricsCiLISIlabelASW), pattern = "/broad/", replacement = "/")

dir.create("broad/CiLISIlabelASW/singleTask",recursive = T)
dir.create("broad/CiLISIlabelASW/best")

write.csv(metricsCiLISIlabelASW,"broad/CiLISIlabelASW/metrics.csv",col.names = T)


plotBestMethodsRNA(
  csv_metrics_path = "broad/CiLISIlabelASW/metrics.csv",
  outdir = "broad/CiLISIlabelASW/",
  # csv_usability_path = "./data/usability4bestMethods.csv",
  #csv_scalability_time_path = "./scalability_score_time_revision.csv",
  #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
  ids_RNA = c("lung_atlas","immune_cell_hum", "tcells_atlas"),
  #ids_simulation = c("simulations_1_1", "simulations_2"),  
  labels_RNA = c("Lung","Immune (hum)" ,"T cells" ),
  #labels_simulation = c("Sim 1", "Sim 2"), 
  weight_batch = 0.4,
  keepBest = F, keepBestOutput = F
)


plotBestMethodsRNA(
  csv_metrics_path = "broad/CiLISIlabelASW/metrics.csv",
  outdir = "broad/CiLISIlabelASW/best",
  # csv_usability_path = "./data/usability4bestMethods.csv",
  #csv_scalability_time_path = "./scalability_score_time_revision.csv",
  #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
  ids_RNA = c("immune_cell_hum", "tcells_atlas"),
  #ids_simulation = c("simulations_1_1", "simulations_2"),  
  labels_RNA = c("Immune (hum)" ,"T cells" ),
  #labels_simulation = c("Sim 1", "Sim 2"), 
  weight_batch = 0.4,
  keepBest = T, keepBestOutput = T
)



plotSingleTaskRNA("broad/CiLISIlabelASW/metrics.csv",outdir = "broad/CiLISIlabelASW/singleTask")

```

```{r}
# To show shrinkage of scaled score because of fastmnn full output

# metricsCiLISIlabelASW_all <- metrics[,c("CiLISI","ASW_label")]
# 
# #metricsCiLISIlabelASW <- metricsCiLISIlabelASW[,c("CiLISI","ASW_label_raw")] 
# 
# #metricsCiLISIlabelASW$ASW_label_raw[metricsCiLISIlabelASW$ASW_label_raw < 0] <- 0
# 
# colnames(metricsCiLISIlabelASW_all) <- c("iLISI","ASW_label")
# dir.create("CiLISIlabelASW_all/singleTask",recursive = T)
# dir.create("CiLISIlabelASW_all/best")
# 
# 
# rownames(metricsCiLISIlabelASW_all) <- gsub(rownames(metricsCiLISIlabelASW_all), pattern = "/unknown_15_shuffling_20/", replacement = "/")
# 
# 
# 
# write.csv(metricsCiLISIlabelASW_all,"CiLISIlabelASW_all/metrics.csv",col.names = T)
# 
# 
# plotBestMethodsRNA(
#   csv_metrics_path = "CiLISIlabelASW_all/metrics.csv",
#   outdir = "CiLISIlabelASW_all",
#   # csv_usability_path = "./data/usability4bestMethods.csv",
#   #csv_scalability_time_path = "./scalability_score_time_revision.csv",
#   #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
#   ids_RNA = c("human_pancreas", "lung_atlas", "immune_cell_hum","immune_cell_hum_mou","tcells_atlas"),
#   #ids_simulation = c("simulations_1_1", "simulations_2"),  
#   labels_RNA = c("Pancreas", "Lung", "Immune (hum)",'Immune (hum, mou)', 'T cells'),
#   #labels_simulation = c("Sim 1", "Sim 2"), 
#   weight_batch = 0.4,
#   keepBest = F, keepBestOutput = F
# )
# 
# 
# plotBestMethodsRNA(
#   csv_metrics_path = "CiLISIlabelASW_all/metrics.csv",
#   outdir = "CiLISIlabelASW_all/best",
#   # csv_usability_path = "./data/usability4bestMethods.csv",
#   #csv_scalability_time_path = "./scalability_score_time_revision.csv",
#   #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
#   ids_RNA = c("human_pancreas", "lung_atlas", "immune_cell_hum","immune_cell_hum_mou","tcells_atlas"),
#   #ids_simulation = c("simulations_1_1", "simulations_2"),  
#   labels_RNA = c("Pancreas", "Lung", "Immune (hum)",'Immune (hum, mou)', 'T cells'),
#   #labels_simulation = c("Sim 1", "Sim 2"), 
#   weight_batch = 0.4,
#   keepBest = T, keepBestOutput = T
# )
# 
# 
# 
# plotSingleTaskRNA("CiLISIlabelASW_all/metrics.csv",outdir = "CiLISIlabelASW_all/singleTask")

```

```{r}
oriMetrics <- colnames(read.csv("../data/metrics.csv",row.names = 1))
oriMetrics <- oriMetrics[oriMetrics != "hvg_overlap"]

metricsMethodOK <- metrics[!metrics$method %in% c("seuratrpca_full","semiSupSTACAS_full","STACAS_full","seurat_full","fastmnn_full")& metrics$noise == "unknown_15_shuffling_20",
                           oriMetrics]

#metricsCiLISIlabelASW <- metricsCiLISIlabelASW[,c("CiLISI","ASW_label_raw")] 

#metricsCiLISIlabelASW$ASW_label_raw[metricsCiLISIlabelASW$ASW_label_raw < 0] <- 0

rownames(metricsMethodOK) <- gsub(rownames(metricsMethodOK), pattern = "/unknown_15_shuffling_20/", replacement = "/")



dir.create("unknown_15_shuffling_20/oriMetrics/singleTask",recursive = T)
dir.create("unknown_15_shuffling_20/oriMetrics/best")

write.csv(metricsMethodOK,"unknown_15_shuffling_20/oriMetrics/metrics.csv",col.names = T)


plotBestMethodsRNA(
  csv_metrics_path = "unknown_15_shuffling_20/oriMetrics/metrics.csv",
  outdir = "unknown_15_shuffling_20/oriMetrics",
  # csv_usability_path = "./data/usability4bestMethods.csv",
  #csv_scalability_time_path = "./scalability_score_time_revision.csv",
  #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
  ids_RNA = tasks,
  #ids_simulation = c("simulations_1_1", "simulations_2"),  
  labels_RNA = labels,
  #labels_simulation = c("Sim 1", "Sim 2"), 
  weight_batch = 0.4,
  keepBest = F, keepBestOutput = F
)


plotBestMethodsRNA(
  csv_metrics_path = "unknown_15_shuffling_20/oriMetrics/metrics.csv",
  outdir = "unknown_15_shuffling_20/oriMetrics/best",
  # csv_usability_path = "./data/usability4bestMethods.csv",
  #csv_scalability_time_path = "./scalability_score_time_revision.csv",
  #csv_scalability_memory_path = "./scalability_score_memory_revision.csv",
  ids_RNA = tasks,
  #ids_simulation = c("simulations_1_1", "simulations_2"),  
  labels_RNA = labels,
  #labels_simulation = c("Sim 1", "Sim 2"), 
  weight_batch = 0.4,
  keepBest = T, keepBestOutput = T
)



plotSingleTaskRNA("unknown_15_shuffling_20/oriMetrics/metrics.csv",outdir = "unknown_15_shuffling_20/oriMetrics/singleTask")

```