---
title: "Zoom in on differences between STACAS and scANVI"
author: "Leonard Herault"
date: '2023-25-09'
output: html_document
---

```{r}
library(ggplot2)
```

Analyze differences between ssSTACAS and scANVI rankings
```{r}
tasks <- c("human_pancreas", "lung_atlas", "immune_cell_hum","tcells_atlas")
all.task.scores <- data.frame()
for (t in tasks) {
  task.scores <- read.csv(paste0("unknown_15_shuffled_20/oriMetrics/singleTask/",t,"_summary_scores.csv") )
  task.scores <- task.scores[,which(colnames(task.scores)!= "trajectory.conservation")]
  task.scores$task <- t
  all.task.scores <- rbind(all.task.scores,task.scores)
}

all.task.scores$method_output <- paste0(all.task.scores$Method,"_",all.task.scores$Output)
all.task.scores$method_full <- paste0(all.task.scores$method,"_",all.task.scores$Scaling)

```

```{r}
palette <-  c(RColorBrewer::brewer.pal(n=12, name="Paired"), RColorBrewer::brewer.pal(n=12, name="Set3"))
#remove yellows
palette <- palette[!palette %in% c("#FFFF99","#FFFFB3","#FFED6F")]



methodToCompare <- c("STACAS_embed",
                     "ssSTACAS*_embed",
                     "Seurat v4 RPCA_embed",
                     "Seurat v4 CCA_embed",
                     "fastMNN_embed",
                     "Harmony_embed",
                     "scVI_embed", 
                     "Scanorama_embed",
                     "scANVI*_embed", 
                     "ComBat_gene",
                     "scGen*_gene",
                     "Unintegrated_gene"
)


all.task.scores.kept.methods <-  all.task.scores[all.task.scores$method_output %in% methodToCompare,]

all.task.scores.kept.methods$Method <- factor(all.task.scores.kept.methods$Method)

names(palette) <- c("ComBat","FastMNN","Harmnoy","Scanorama","scANVI*","scGen*","scVI","ssSTACAS*","Seurat v4 CCA","Seurat v4 RPCA","STACAS","Unintegrated")




```

# Boxplot for Overall.Score (60% Bio.conservation, 40% Batch.correction)
All methods present in figure 3 ABCD, scaled/unscaled.
ssSTACAS\*_embed_unscaled, scANVI\*_embed_unscaled are highlighted.

```{r}
p_overall <- ggplot() + geom_boxplot(data = all.task.scores.kept.methods,
                        aes(x=task,y=Overall.Score),inherit.aes = F) +
  geom_point(data = all.task.scores.kept.methods[all.task.scores.kept.methods$Method %in%
                                                   c("ssSTACAS*","scANVI*","Unintegrated") &
                                                   all.task.scores.kept.methods$Scaling == "unscaled",],
       aes(x=task,y=Overall.Score,color = Method,group = method_full),size = 2) +
  geom_line(data =  all.task.scores.kept.methods[all.task.scores.kept.methods$Method %in%
                                                   c("ssSTACAS*","scANVI*","Unintegrated") &
                                                   all.task.scores.kept.methods$Scaling == "unscaled",],
       aes(x=task,y=Overall.Score,color = Method,group = method_full)) + 
  scale_color_manual(values=palette) + 
  scale_shape_manual(values = 17) +
  theme_minimal()

p_overall
```


# Boxplot for Bio.conservation scores
All methods present in figure 3 ABCD, scaled/unscaled.
ssSTACAS\*_embed_unscaled, scANVI\*_embed_unscaled and Unintegrated are highlighted.

```{r}
p_bio <- ggplot() +
  geom_boxplot(data = all.task.scores.kept.methods,  aes(x=task,y=Bio.conservation),inherit.aes = F) +
  geom_point(data = all.task.scores.kept.methods[all.task.scores.kept.methods$Method %in%
                                                   c("ssSTACAS*","scANVI*","Unintegrated") &
                                                   all.task.scores.kept.methods$Scaling == "unscaled",],
       aes(x=task,y=Bio.conservation,color = Method,group = method_full),size = 2) +
  geom_line(data =  all.task.scores.kept.methods[all.task.scores.kept.methods$Method %in%
                                                   c("ssSTACAS*","scANVI*","Unintegrated") &
                                                   all.task.scores.kept.methods$Scaling == "unscaled",],
       aes(x=task,y=Bio.conservation,color = Method,group = method_full)) + 
  scale_color_manual(values=palette) + 
  scale_shape_manual(values = 17) +
  theme_minimal()

p_bio
```
# Boxplot for Batch.Correction scores
All methods present in figure 3 ABCD), scaled/unscaled.
ssSTACAS\*_embed_unscaled, scANVI\*_embed_unscaled are highlighted.

```{r}
p_batch <- ggplot() + geom_boxplot(data = all.task.scores.kept.methods,
                                   aes(x=task,y=Batch.Correction),inherit.aes = F) +
  geom_point(data = all.task.scores.kept.methods[all.task.scores.kept.methods$Method %in%
                                                   c("ssSTACAS*","scANVI*","Unintegrated") &
                                                   all.task.scores.kept.methods$Scaling == "unscaled",],
       aes(x=task,y=Batch.Correction,color = Method,group = method_full),size = 2) +
  geom_line(data =  all.task.scores.kept.methods[all.task.scores.kept.methods$Method %in%
                                                   c("ssSTACAS*","scANVI*","Unintegrated") &
                                                   all.task.scores.kept.methods$Scaling == "unscaled",],
       aes(x=task,y=Batch.Correction,color = Method,group = method_full)) + 
  scale_color_manual(values=palette) + 
  scale_shape_manual(values = 17) +
  theme_minimal()

p_batch
```

```{r fig.width=12, fig.height=5}
library(patchwork)

(p_overall | p_batch | p_bio) & theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("pdf/scANVI_vs_STACAS_boxplots.pdf", height=4, width=9)
```

# All Bio.conservation metrics for the pancreas task
```{r fig.width=8}
library(patchwork)
Bio.conservation.metrics <- c("NMI.cluster.label",
                              "ARI.cluster.label",
                              "isolated.label.F1",
                              "isolated.label.silhouette",
                              "graph.cLISI","
                              CC.conservation")
  
pancreas.task <- all.task.scores.kept.methods[all.task.scores.kept.methods$task == "human_pancreas",]

pll <- lapply(Bio.conservation.metrics, function(m) {
  ggplot() + geom_boxplot(data = pancreas.task,  aes_string(x="task",y=m),inherit.aes = F) +
  geom_point(data = pancreas.task[pancreas.task$Method %in%
                                    c("ssSTACAS*","scANVI*","Unintegrated") &
                                    pancreas.task$Scaling == "unscaled",],
       aes_string(x="task",y=m,color = "Method",group = "method_full"),size = 3) +
  scale_color_manual(values=palette) + 
  scale_shape_manual(values = 17) + ylim(c(0,1)) +
  theme_minimal()
})
wrap_plots(pll)
```
scANVI* performs particularly bad for CC.conservation (lower than unintegrated approach). Also visible in the [ranking plot for pancreas task](unknown_15_shuffled_20/oriMetrics/singleTask/20230705_131027_human_pancreas_summary_metrics.pdf).

#Other benchmark

##Results in CiLISI vs ASW
ssSTACAS* is better than scANVI* for both metrics in Pancreas, Lung and Immune tasks (50 components, figures 3 ABC in manuscript).
ssSTACAS* is better for ASW than scANVI* but a little bit lower for CiLISI than scANVI* in T cells tasks (manuscript figure 3 D). 
ssSTACAS* is better than scANVI* for overall score in all tasks with 30 and 50 components (figures S2 B and D in manuscript)

##Results in overall score for original metrics with 30 components
Results shown in manuscript fig S2
ssSTACAS* (final rank 1) is better than scANVI* in Pancreas and Immune task.
scANVI* (final rank 2) is better than ssSTACAS* in Lung and T cells.



