---
title: "Benchmark supervised tools with nearest-neighbor label shuffling 50 comp"
author: "Leonard Herault"
date: '2022-12-09'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r cars}
library(ggplot2)
library(Seurat)
library(ggrepel)
```


```{r}
library(tibble)
library(RColorBrewer)
library(dynutils)
library(stringr)
library(Hmisc)
library(plyr)
# library(scIntegrationMetrics)
library(anndata)
```

```{r}
#Move to directory of this script
#setwd("./results/sensitivity_analysis_shuffling_neighbors")

source("../knit_table.R") 
source("../R_fun_report.R")
```



This report requires the files :

-   `../../sensitivity_analysis_subtype_wrongly_assigned_50_comp/metrics_R.csv`
-   `../../sensitivity_analysis_subtype_wrongly_assigned_50_comp/metrics.csv`

generated with the snakemake pipeline using the config file `configs/original_annotations-R4.1.yaml`.
First we copy them in the current directory (these file are already provided here in the repository)

**To be noted that seurat_rpca broke for rm8 and rm9 (scaled and unscaled).**

```{r}
if (!file.exists("./metrics_R.csv")) {
  file.copy("../../sensitivity_analysis_shuffling_neighbors_50_comp/metrics_R.csv","./")
}

if (!file.exists("./metrics.csv")) {
  file.copy("../../sensitivity_analysis_shuffling_neighbors_50_comp/metrics.csv","./")
}

```






```{r}
metricsR <- read.csv("metrics_R.csv",row.names = 1)

scenarios <- str_split_fixed(rownames(metricsR),pattern = "/",n=7)
#head(scenarios)

scenarios <- scenarios[,-1]
colnames(scenarios) <- c("task","annotations","folder","scaling","features","method")
metricsR <- cbind(scenarios,metricsR)

metricsR$method <- str_split_fixed(metricsR$method,pattern = "/",n=2)[,2]
metricsR$output <- str_split_fixed(metricsR$method,pattern = "_",n=2)[,2]
metricsR$tool <- str_split_fixed(metricsR$method,pattern = "_",n=2)[,1]

metricsR_previous <- read.csv("../final_benchmark_50_comp/metrics_R.csv",row.names = 1)


scenarios_previous <- str_split_fixed(rownames(metricsR_previous),pattern = "/",n=7)
#head(scenarios_previous)

scenarios_previous <- data.frame(scenarios_previous[,-1])

colnames(scenarios_previous) <- c("task","annotations","folder","scaling","features","method")
scenarios_previous$method <- str_split_fixed(scenarios_previous$method,pattern = "/",n=2)[,2]



keptIndex <- which((scenarios_previous$scaling %in% c("unscaled") & scenarios_previous$task %in% c("immune_cell_hum","human_pancreas","tcells_atlas","lung_atlas")) &
                     (scenarios_previous$method %in% c("scgen_full","semiSupSTACAS_embed","STACAS_embed","scanvi_embed","scvi_embed","unintegrated_full")&
                        scenarios_previous$annotations == "unknown_15_shuffled_20"))

rn <- rownames(metricsR_previous)[keptIndex]

metricsR_previous <- cbind(scenarios_previous[keptIndex,],metricsR_previous[keptIndex,])
rownames(metricsR_previous) <- rn

metricsR_previous$output <- str_split_fixed(metricsR_previous$method,pattern = "_",n=2)[,2]
metricsR_previous$tool <- str_split_fixed(metricsR_previous$method,pattern = "_",n=2)[,1]


metricsR <- rbind(metricsR,metricsR_previous[,colnames(metricsR)])
```



```{r}
metrics <- read.csv("metrics.csv",row.names = 1)

scenarios <- str_split_fixed(rownames(metrics),pattern = "/",n=7)
#head(scenarios)

scenarios <- scenarios[,-1]
colnames(scenarios) <- c("task","annotations","folder","scaling","features","method")
metrics <- cbind(scenarios,metrics)

#metrics$method <- str_split_fixed(metrics$method,pattern = "/",n=2)[,2]
metrics$output <- str_split_fixed(metrics$method,pattern = "_",n=2)[,2]
metrics$tool <- str_split_fixed(metrics$method,pattern = "_",n=2)[,1]

metrics_previous <- read.csv("../final_benchmark_50_comp/metrics.csv",row.names = 1)

scenarios_previous <- str_split_fixed(rownames(metrics_previous),pattern = "/",n=7)
#head(scenarios_previous)

scenarios_previous <- data.frame(scenarios_previous[,-1])

colnames(scenarios_previous) <- c("task","annotations","folder","scaling","features","method")
#scenarios_previous$method <- str_split_fixed(scenarios_previous$method,pattern = "/",n=2)[,2]



keptIndex <- which((scenarios_previous$scaling %in% c("unscaled") & scenarios_previous$task %in% c("immune_cell_hum","human_pancreas","tcells_atlas","lung_atlas")) &
                     (scenarios_previous$method %in% c("scgen_full","semiSupSTACAS_embed","STACAS_embed","scanvi_embed","scvi_embed","unintegrated_full")&
                        scenarios_previous$annotations == "unknown_15_shuffled_20"))

rn <- rownames(metrics_previous)[keptIndex]


metrics_previous <- cbind(scenarios_previous[keptIndex,],metrics_previous[keptIndex,])

rownames(metrics_previous) <- rn

metrics_previous$output <- str_split_fixed(metrics_previous$method,pattern = "_",n=2)[,2]
metrics_previous$tool <- str_split_fixed(metrics_previous$method,pattern = "_",n=2)[,1]


metrics <- rbind(metrics,metrics_previous[,colnames(metrics)])
```


Compared to first analysis results with original annotations, we only analysed unscaled scenarios
```{r}
#TO DO will be removed from results and config file as it is now in the final_benchmark config
metrics <- metrics[metrics$scaling == "unscaled",]
metricsR <- metricsR[metricsR$scaling == "unscaled",]
```



```{r}
rownames(metricsR) <- gsub(rownames(metricsR),pattern = "/R/",replacement = "/")

metrics <- cbind(metrics, metricsR[rownames(metrics),c("CiLISI","CiLISI_means")])

#Set annotation for unsup tools to original for clarity
metrics[(metrics$method %in% c("STACAS_embed","scvi_embed","unintegrated_full") & metrics$annotations == "unknown_15_shuffled_20"),"annotations"] <- "original" 

metrics$ASW_label_raw <- 2*metrics$ASW_label-1


```



## Comparison with previous noise
```{r}
#metrics.shuffled.neighbors <- metrics[!startsWith(metrics$annotations,"merging"),  ]

ggplot(metrics[metrics$annotations %in% c("shuffledWithGuide_20","original","unknown_15_shuffled_20"),],aes(x=CiLISI,y=ASW_label_raw,color = method,shape = annotations)) + geom_point(size = 3) + facet_wrap("~task")
```
# Increased neighbor shuffling

## ASW label score

```{r fig.width=10, fig.height=2.5}
pdir <- "pdf/overfitting"
dir.create(pdir,recursive = T)

palette <- c("#FF3333","#FF9999","#FFFF00","#996633","#FFCC66","#99CCCC")
names(palette) <- c("semiSupSTACAS_embed","scanvi_embed","scgen_full","STACAS_embed","scvi_embed","unintegrated_full")
shapes <- c(19,19,19,9,9,9)
names(shapes) <- names(palette)

metrics$annotations <- factor(metrics$annotations,levels = c("original", "shuffledWithGuide_5",    "shuffledWithGuide_10",   "shuffledWithGuide_15",  "shuffledWithGuide_20",   "shuffledWithGuide_25"  , "shuffledWithGuide_30" ,  "shuffledWithGuide_35" , "shuffledWithGuide_40" ,  "shuffledWithGuide_45"  , "shuffledWithGuide_50" ,  "shuffledWithGuide_60"  ,
"shuffledWithGuide_70" ,  "shuffledWithGuide_80"  , "shuffledWithGuide_90" ,  "shuffledWithGuide_100" ))
metrics$ASW_label_raw <- 2*metrics$ASW_label-1

data <- metrics[grepl(metrics$annotations,pattern = "shuffledWithGuide|original"),]
data$method <- factor(data$method, levels=names(palette))

ggplot(data, aes(x = annotations,color=method,y=ASW_label_raw,group = method)) +
  geom_point(aes(shape=method)) + geom_line() +  facet_wrap('~task', scales="free", ncol=4) + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  scale_color_manual(values=palette) +
  scale_shape_manual(values=shapes)

ggsave(sprintf("%s/effect_of_shuffling_ss.pdf", pdir), height=2.5, width=10)
```


```{r fig.width=10, fig.height=2.5}
pdir <- "pdf/overfitting"
dir.create(pdir,recursive = T)

palette <- c("#FF3333","#FF9999","#FFFF00","#996633","#FFCC66","#99CCCC")
names(palette) <- c("semiSupSTACAS_embed","scanvi_embed","scgen_full","STACAS_embed","scvi_embed","unintegrated_full")
shapes <- c(19,19,19,9,9,9)
names(shapes) <- names(palette)

data <- metrics[grepl(metrics$annotations,pattern = "shuffledWithGuide_|original"),]

data$neighbor_shuffling <- str_split_fixed(data$annotations,pattern = "_",2)[,2]

data$neighbor_shuffling[data$annotations == "original"] <- 0
data <- data[as.numeric(data$neighbor_shuffling) <= 50, ]  #only makes sense up to 50% shuffle

levs <- sort(unique(as.numeric(data$neighbor_shuffling)))
data$neighbor_shuffling <- factor(data$neighbor_shuffling, levels = as.character(levs))

data$ASW_label_raw <- 2*data$ASW_label-1

data$method <- factor(data$method, levels=names(palette))


ggplot(data,
       aes(neighbor_shuffling,color=method,y=ASW_label_raw, group = method)) +
  geom_point(aes(shape=method)) + geom_line() +  facet_wrap('~task', scales="free", ncol=4) + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  scale_color_manual(values=palette) +
  scale_shape_manual(values=shapes)

a <- ggsave(sprintf("%s/effect_of_shuffling_ss.pdf", pdir), height=2.5, width=10)
a
```

```{r fig.width=10, fig.height=2.5}
ggplot(data,
       aes(neighbor_shuffling,color=method,y=CiLISI, group = method)) +
  geom_point(aes(shape=method)) + geom_line() +  facet_wrap('~task', scales="free", ncol=4) + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  scale_color_manual(values=palette) +
  scale_shape_manual(values=shapes)

a <- ggsave(sprintf("%s/effect_of_shuffling_CiLISI.pdf", pdir), height=2.5, width=10)
a
```

## Checking introduced noise

```{r}
# adata <- read_h5ad("../../sensitivity_analysis_shuffling_neighbors_50_comp//human_pancreas/shuffledWithGuide_45/metrics/unscaled/hvg/scgen_full.h5ad")
# colnames(adata$obs)
# 
# table(adata$obs$celltype,adata$obs$shuffledWithGuide_45_celltype)

```
